Body Image and Trikafta

### 2024-06-24 Emily Muther/body_image_trikafta.qmd
body image and trikafta added ranges, etc.

```{r}
#| label: demographics
normal_dist <- c("FRS_IdealBody")
df %>%
  select(
    PHQ9_Total, PHQ9_category, GAD7_Total, GAD7_category, FRStotal,
    FRS_IdealBody, FRS_ThinkyouLook, FRS_Category, Age, Gender, Race,
    Ethnicity
  ) %>%
  tbl_summary(
    by = Gender,
    type = list(c("FRStotal", "FRS_IdealBody", "FRS_ThinkyouLook") ~
      "continuous"),
    statistic = list(all_of(normal_dist) ~ "{mean} [{sd}]"),
    missing_text = "(Missing)"
  ) %>%
  add_overall() %>%
  add_p(
    test = list(all_of(normal_dist) ~ "t.test"),
    test.args = all_tests("wilcox.test") ~ list(exact = F)
  ) %>%
  separate_p_footnotes()
```

@@

>>>>

```{r}
#| label: demographics
normal_dist <- c("FRS_IdealBody", "FEV1")
df %>%
  select(
    PHQ9_Total, PHQ9_category, GAD7_Total, GAD7_category, FRStotal,
    FRS_IdealBody, FRS_ThinkyouLook, FRS_Category, Age, Gender, Race,
    Ethnicity, InsuranceType, BMI, FEV1
  ) %>%
  tbl_summary(
    by = Gender,
    type = list(
      c("FRStotal", "FRS_IdealBody", "FRS_ThinkyouLook") ~ "continuous2",
      all_continuous() ~ "continuous2"
    ),
    statistic = list(
      all_continuous() ~ c(
        "{median} ({p25}, {p75})",
        "{min}, {max}"
      ),
      all_of(normal_dist) ~ "{mean} [{sd}]"
    ),
    missing_text = "(Missing)"
  ) %>%
  add_overall() %>%
  add_p(
    test = list(all_of(normal_dist) ~ "t.test"),
    test.args = all_tests("wilcox.test") ~ list(exact = F)
  ) %>%
  separate_p_footnotes()
# Skim (so Emily can see distributions)
df %>%
  select(
    PHQ9_Total, PHQ9_category, GAD7_Total, GAD7_category, FRStotal,
    FRS_IdealBody, FRS_ThinkyouLook, FRS_Category, Age, Gender, Race,
    Ethnicity, InsuranceType, BMI, FEV1
  ) %>%
  skimr::skim()
```

@@

## Adherence

```{r}
#| label: adherence
df %>%
  select(contains("Adherence"), FRS_Category) %>%
  mutate(
    PercentAdherence = as.numeric(sub("%", "", as.character(PercentAdherence))),
    over80 = PercentAdherence >= 80
  ) %>%
  tbl_summary(
    by = "FRS_Category",
    type = list("PercentAdherence" ~ "continuous"),
    missing_text = "(Missing)"
  ) %>%
  add_overall() %>%
  add_p() %>%
  separate_p_footnotes()
```
